---
title: "Summarize REFLORA collections"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{1 Summarize REFLORA collections}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Here in this article, we show how to use the package's function `reflora_summary` for summarizing informnation about all REFLORA-associated collections.\
\

# Setup
\
Install the latest development version of ***refloraR*** from 
[GitHub](https://github.com/DBOSlab/refloraR):\
\

``` r
#install.packages("devtools")
devtools::install_github("DBOSlab/refloraR")
```
```{r package load, message=FALSE, warning=FALSE}
library(refloraR)
```

\
The following code can be used to extract a summary of all REFLORA-associated collections, including herbarium acronym, curator's email contact, number of records and a direct link to the original REFLORA Integrated Publishing Toolkit ([IPT](https://ipt.jbrj.gov.br/reflora)).\
\

```r
summary_df <- reflora_summary(verbose = TRUE,
                              save = TRUE,
                              dir = "reflora_summary")
```

\
By specifying a vector of herbarium acronyms, the user can extract a summary for just the specific herbarium collection.\
\

```r
summary_some_df <- reflora_summary(herbarium = c("ALCB", "RB", "HUEFS", "US", "K"),
                                   verbose = TRUE,
                                   save = TRUE,
                                   dir = "reflora_summary")
```

