---
title: "Download REFLORA specimen records"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{2 Download REFLORA specimen records}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Here in this article, we show how to use the package's function `reflora_download` for downloading all original herbarium specimen records from REFLORA Integrated Publishing Toolkit ([IPT](https://ipt.jbrj.gov.br/reflora)).\
\

# Setup
\
Install the latest development version of ***refloraR*** from 
[GitHub](https://github.com/DBOSlab/refloraR):\
\

``` r
#install.packages("devtools")
devtools::install_github("DBOSlab/refloraR")
```
```{r package load, message=FALSE, warning=FALSE}
library(refloraR)
```

\
The following code can be used to download original specimen records in Darwin Core Format and associated metada for all REFLORA collections.\
\

```r
reflora_download(verbose = TRUE,
                 dir = "reflora_download")
```

\
By specifying a vector of herbarium acronyms, the user can download specimens records for just the specific herbarium collection.\
\

```r
reflora_download(herbarium = c("ALCB", "HUEFS", "RB", "US", "K"),
                 verbose = TRUE,
                 dir = "reflora_download")
```

